---
title: "R Notebook"
output: html_notebook
---

* Events:

**5th July 2017**

As Americans relaxed over a long Fourth of July weekend, the pro-Trump meme factories were gearing up for war.
https://www.nytimes.com/2017/07/05/business/how-a-cnn-investigation-set-off-an-internet-meme-war.html

**15th September 2017**

September 14
On September 14, conservative radio host Ben Shapiro gave a speech at the campus, which was covered by a crew for the political documentary No Safe Spaces.
https://en.wikipedia.org/wiki/2017_Berkeley_protests

News of Donald Trump reaching a possible **DACA deal** with Democratic congressional leaders has infuriated members of the alt-right. 
https://mashable.com/2017/09/15/donald-trump-daca-alt-right-burn-maga-hat/#KjqWZV4nekqN

**September 29, 2017**

Evangelical leaders call on Trump to condemn the alt-right
https://religionnews.com/2017/09/29/in-rare-letter-evangelical-leaders-call-on-trump-to-condemn-the-alt-right/

**9th December 2017**

This Saturday, a handful of demonstrations took place across the US that in several instances broke out into violent clashes between those on the far-Right and antifascists. On Saturday, December 9th, demonstrations and clashes broke out in a select few cities, including Portland, Oregon, San Diego, California, and Austin, Texas. Neo-Nazis who attended the Unite the Right rally in Charlottesville, VA.
https://itsgoingdown.org/audio-report-austin-antifascists-mobilize-far-right/



# load in packages

```{r}
pacman::p_load(tidyverse, highcharter, magrittr)
```


# vizz

## media data

```{r}
# social_media <- get(load("data/abc.Rdata")) %>% 
#   bind_rows(get(load("data/msnbc.Rdata"))) %>% 
#   bind_rows(get(load("data/foxnews.Rdata"))) %>% 
#   bind_rows(get(load("data/cnn.Rdata")))
```

## media

## Case Study: Unite the Right Charlottesville Rally

```{r}
library(highcharter)
library(magrittr)

load("data/dat_time_xts.Rdata")

```


```{r}

dat_time_xts %>% 
  filter(platform == "Twitter") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis")) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)
```

---

## Case Study: Unite the Right Charlottesville Rally

```{r}
dat_time2 <- dat_time_xts %>%
  filter(cdate > as.Date("2017-08-06") & cdate < as.Date("2017-08-30")) 


dat_time2 %>% 
  filter(platform == "Twitter") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis"),
           plotLines = list(
             list(label = list(text = "Unite the Right Rally"),
                  color = "gray70",
                  width = 2,
                  value = datetime_to_timestamp(as.Date("2017-08-11")))),
            plotBands = list(
                list(
                  label = list(text = ""),
                  color = "rgba(100, 0, 0, 0.1)",
                  from = datetime_to_timestamp(as.Date("2017-08-11")),
                  to = datetime_to_timestamp(as.Date("2017-08-12"))
               )
            )) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)


```


---

## Case Study: Unite the Right Charlottesville Rally

```{r}

dat_time_xts %>% 
  filter(platform == "YouTube") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis")) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)
```


---

## Case Study: Unite the Right Charlottesville Rally

```{r}
 

dat_time2 %>% 
  filter(platform == "YouTube") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - YouTube",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis"),
           plotLines = list(
             list(label = list(text = "Unite the Right Rally"),
                  color = "gray70",
                  width = 2,
                  value = datetime_to_timestamp(as.Date("2017-08-11")))),
            plotBands = list(
                list(
                  label = list(text = ""),
                  color = "rgba(100, 0, 0, 0.1)",
                  from = datetime_to_timestamp(as.Date("2017-08-11")),
                  to = datetime_to_timestamp(as.Date("2017-08-12"))
               )
            )) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)




```

#### old

```{r, fig.width=15}


dat_time_whole <- social_media %>%
  #sample_n(size = 10000) %>%
  filter(platform != "fb") %>%
  group_by(platform, page, cdate) %>%
  #tally() %>%
  count(pred1) %>%
  mutate(perc = n/sum(n)) %>%
  ungroup()

# gg1 <- dat_time_whole %>%
# #  filter(!(page == "wapo" & platform == "yt" & cdate < as.Date("2017-06-01"))) %>%
#   filter(pred1 == 1) %>%
#   ggplot(aes(cdate, perc)) +
#   geom_line() +
#   scale_x_date() +
#   facet_grid(page  ~ platform, scales = "free") +
#   ggthemes::theme_hc() +
#   geom_vline(xintercept = as.Date("2017-08-12"), color = "red") +
#     geom_vline(xintercept = as.Date("2017-01-20"), color = "red")
# #ggsave(gg1, file = "gg_time_all_media.png", width = 10)
# gg1


dat_time_xts <- dat_time_whole %>%
  mutate(perc = round(100*perc, 2)) %>% 
  mutate(platform = case_when(
      platform == "fb" ~ "Facebook",
      platform == "tw" ~ "Twitter",
      platform == "yt" ~ "YouTube"
    )
  ) %>%
    mutate(page = forcats::fct_recode(page, 
                                    `CNN` = "cnn",
                                    `ABC` = "abc",
                                    `MSNBC` = "msnbc",
                                    `New York Times` = "nyt",
                                    `Washington Post` = "wapo",
                                    `Fox News` = "foxnews"
                                    )) %>% 
  filter(platform != "fb") %>%
  # filter(sent == 0) %>%
  filter(pred1 == 1) %>%
  na.omit() 

save(dat_time_xts, file = "slides/data/dat_time_xts.Rdata")
load("slides/data/dat_time_xts.Rdata")



dat_time_xts %>% 
  filter(platform == "YouTube") %>% 
  chart_all() %>% 
      hc_title(text = "Percentage of Classified Comments per Day - YouTube",
             style = list(fontSize = "18px")) 


dat_time_xts %>% 
  filter(platform == "Twitter") %>% 
  chart_all() %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) 


```



#### Timeline 1112


```{r}
dat_time2 <- dat_time_xts %>%
  filter(cdate > as.Date("2017-08-06") & cdate < as.Date("2017-08-30")) 




# gg2 <- dat_time2 %>%
#   filter(pred1 == 1) %>%
#   ggplot(aes(cdate, perc)) +
#   #geom_smooth(se=F) +
#   geom_line(alpha = .5) +
#   #scale_x_date() +
#   facet_grid(page  ~ platform, scales="free") +
#   ggthemes::theme_hc() +
#   geom_vline(xintercept = as.Date("2017-08-11"), color = "red")
#   #geom_vline(xintercept = as.Date("2017-01-20"), color = "red")
# #ggsave(gg2, file = "gg_charl.png", width = 10)
# gg2
```



# highcharter
```{r}
library(highcharter)
# dat_time2 %>%
#   # mutate(perc = round(100*perc, 2)) %>% 
#   mutate(platform = case_when(
#       platform == "fb" ~ "Facebook",
#       platform == "tw" ~ "Twitter",
#       platform == "yt" ~ "YouTube"
#     )
#   ) %>%
#     mutate(page = forcats::fct_recode(page, 
#                                     `CNN` = "cnn",
#                                     `ABC` = "abc",
#                                     `MSNBC` = "msnbc",
#                                     `New York Times` = "nyt",
#                                     `Washington Post` = "wapo",
#                                     `Fox News` = "foxnews"
#                                     )) %>% 
#   filter(platform != "fb") %>%
#   # filter(sent == 0) %>%
#   filter(pred1 == 1) -> charlottesville_charter

charlottesville_charter <- dat_time2

save(charlottesville_charter, file = "slides/data/charlottesville_charter.Rdata")



charlottesville_charter %>% 
  filter(platform == "Twitter") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis"),
           plotLines = list(
             list(label = list(text = "Unite the Right Rally"),
                  color = "gray70",
                  width = 2,
                  value = datetime_to_timestamp(as.Date("2017-08-11")))),
            plotBands = list(
                list(
                  label = list(text = ""),
                  color = "rgba(100, 0, 0, 0.1)",
                  from = datetime_to_timestamp(as.Date("2017-08-11")),
                  to = datetime_to_timestamp(as.Date("2017-08-12"))
               )
            ))


charlottesville_charter %>% 
  filter(platform == "YouTube") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - YouTube",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis"),
           plotLines = list(
             list(label = list(text = "Unite the Right Rally"),
                  color = "gray70",
                  width = 2,
                  value = datetime_to_timestamp(as.Date("2017-08-11")))),
            plotBands = list(
                list(
                  label = list(text = ""),
                  color = "rgba(100, 0, 0, 0.1)",
                  from = datetime_to_timestamp(as.Date("2017-08-11")),
                  to = datetime_to_timestamp(as.Date("2017-08-12"))
               )
            ))





```

# text


```{r}
cnn <- get(load("data/cnn.Rdata"))

cnn %>% 
  filter(cdate > as.Date("2017-08-08") & cdate < as.Date("2017-08-14")) %>% 
  arrange(desc(pred1)) %>% 
  filter(str_detect(text, "meme|\\(\\(\\("))





cnn %>% 
  filter(cdate > as.Date("2017-07-04") & cdate < as.Date("2017-07-06")) %>% 
  arrange(desc(pred1)) %>% 
  filter(!(str_detect(text, ".lack.ail")))
```


## user

```{r}
cnn <- get(load("data/cnn.Rdata"))

dat_user <- cnn %>%
  filter(!is.na(from)) %>%
  group_by(platform, from, pred1) %>%
  tally() %>%
  filter(pred1 == 1) %>%
  group_by(platform) %>%
  arrange(desc(n)) %>%
  top_n(n = 10) %>%
  #count(predict) %>%
  #mutate(perc = n/sum(n)) %>%
  ungroup()

gg_user <- dat_user %>%
  mutate(from = forcats::fct_reorder2(from, platform, desc(n))) %>%
  ggplot(aes(from, n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(~platform, scales = "free")

ggsave(gg_user, file = "gg_user.png", width = 10)

```


# alt right

```{r}

# x <-  dir("data/altright")[1]
load_data <- function(x) {
  get(load(paste0("data/altright/", x)))
}


altright <- dir("data/altright") %>% 
  as.list() %>% 
  purrr::map(load_data) %>% 
  purrr::reduce(bind_rows)







```

## allt time

```{r}
dat_time_whole_altright <- altright %>%
  #sample_n(size = 10000) %>%
  filter(platform != "fb") %>%
  group_by(platform, page, cdate) %>%
  #tally() %>%
  count(pred1) %>%
  mutate(perc = n/sum(n)) %>%
  ungroup()


dat_time_xts_altright <- dat_time_whole_altright %>%
  mutate(perc = round(100*perc, 2)) %>% 
  mutate(platform = case_when(
      platform == "fb" ~ "Facebook",
      platform == "tw" ~ "Twitter",
      platform == "yt" ~ "YouTube"
    )
  ) %>%
  mutate(page = forcats::fct_recode(page, 
                                    `Milo Yiannopoulos` = "milo",
                                    `Alex Jones/Infowars` = "alexjones",
                                    `Mike Cernovich` = "cernovich",
                                    `Paul Joseph Watson` = "pjw",
                                    `Breitbart` = "breitbart",
                                    `Steven Crowder` = "crowder",
                                    `Rebel Media` = "TheRebelTV",
                                    `Blaire White` = "blaire_white",
                                    `Tommy Robinson` = "robinson",
                                    `Stefan Molyneux/Freedomain Radio` = "molymeme",
                                    `Red Ice TV` = "redicetv",
                                    `Black Pigeon Speaks` = "bps",
                                    `Styxhexenhammer` = "styxenhammer",
                                    `Lauren Southern` = "lauren",
                                    `Baked Alaska` = "bakedalaska",
                                    `Return of Kings` = "returnofkings",
                                    `VDARE` = "vdare",
                                    `Roosh V` = "roosh",
                                    `RamZPaul` = "ramzpaul",
                                    `Brittany Pettibone` = "pettibone",
                                    `Arktos Media` = "arktosmedia",
                                    `Gavin McInnes` = "gavin",
                                    `The National Policy Institute/Radix Journal` = "NPIRadix",
                                    `Millenial Woes` = "mw",
                                    `Roaming Millenial` = "roaming",
                                    `Richard Spencer` = "richardspencer",
                                    `Identity Evropa` = "europa",
                                    `Paul Elam` = "paulelam",
                                    `AltRight.com` = "altright",
                                    `Tara McCarthy` = "tara",
                                    `Counter-Currents` = "countercurr",
                                    `Ann Coulter` = "anncoulter",
                                    `American Renaissance` = "americanrenaissance"
                                    ))  %>% 
  filter(platform != "fb") %>%
  # filter(sent == 0) %>%
  filter(pred1 == 1) %>%
  na.omit() 

save(dat_time_xts_altright, file = "slides/data/dat_time_xts_altright.Rdata")
load("slides/data/dat_time_xts_altright.Rdata")


dat_time_xts_altright %>% 
  filter(platform == "Twitter") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis")) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)

dat_time2 <- dat_time_xts_altright %>%
  filter(cdate > as.Date("2017-08-06") & cdate < as.Date("2017-08-30")) 


dat_time2 %>% 
  filter(platform == "Twitter") %>% 
  highcharter::hchart(., "line", hcaes(x = cdate, y = perc, group = page)) %>% 
      hc_add_theme(hc_theme_google()) %>% 
      hc_title(text = "Percentage of Classified Comments per Day - Twitter",
             style = list(fontSize = "18px")) %>% 
  hc_xAxis(title = list(text = "Days in x Axis"),
           plotLines = list(
             list(label = list(text = "Unite the Right Rally"),
                  color = "gray70",
                  width = 2,
                  value = datetime_to_timestamp(as.Date("2017-08-11")))),
            plotBands = list(
                list(
                  label = list(text = ""),
                  color = "rgba(100, 0, 0, 0.1)",
                  from = datetime_to_timestamp(as.Date("2017-08-11")),
                  to = datetime_to_timestamp(as.Date("2017-08-12"))
               )
            )) %>% 
  hc_yAxis(title = list(text = "Percent")) %>% 
  hc_tooltip(shared = T)
```

